Spatiotemporal Data Classification

### 2018-01-06 Report/BigDataHomeworkPandas.tex
Merge reports

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\todo{Remove the null jids from the start}
	\section{Introduction}
    This is the report related to the Python project for the course "Large-Scale Data Analysis Techniques". In the below sections, the implemented logic will be explicitly analyzed. The project is divided in two parts: in the first part the goals are: to preprocess and clean the given data as well as to visualize five of the given trips in the train\_set file. In the second part, the tasks are: to find for all test trips the k nearest neabours from the given train trips, to find the train trips with the longest similar subroute for each test trip, to use 10-fold cross validation to the training data and classify them with three different methods (k-nearest neighbours, logistic regression and random forest) and finally to choose one of the above classification methods and improve the result.

@@

	\section{Exercise 1}
	In this section, further details are provided related to the preprocessing and cleaning of the training data as well as to the trip's visualization. All files implementing the requirements of this part are in the folder question1.

@@

	The above logic is implemented in the file CleanData.py in function filter\_trips. The two lists (trips\_too\_small and trips\_too\_big) will keep the excluded trips due to either not valid total distance or to invalid max distance between successive points. For each trip in the training dataset (in the dictionary format from question A) the total distance is calculate, using the function calculate\_lonlat\_distance, which returns the distance between two successive points using the haversine formula. Following the same logic, the max distance between successive points of a trip is calculated and a distance is found more than 2km, the trip is excluded.

	Finally, the cleaned trips are kept in a list under the same format that was used in Question A and they are extracted in the file cleanTrips.csv, but also in the file tripsClean.pickle which keeps the data structure used. The functions for the data export are in the file utils.py (write\_trips\_to\_file and write\_trips\_using\_pickle).

>>>>

	\section{Introduction}
    This is the report related to the Python project for the course "Large-Scale Data Analysis Techniques". In the below sections, the implemented logic will be explicitly analyzed. The project is divided in two parts: in the first part the goals are: to preprocess and clean the given data as well as to visualize five of the given trips in the train\_set file. In the second part, the tasks are: to find for all test trips the k nearest neabours from the given train trips, to find the train trips with the longest similar subroute for each test trip, to use 10-fold cross validation to the training data and classify them with three different methods (k-nearest neighbours, logistic regression and random forest) and finally to choose one of the above classification methods and improve the result.

@@

	\section{Exercise 1}
	In this section, further details are provided related to the preprocessing and cleaning of the training data as well as to the trip's visualization. All files implementing the requirements of this part are in the file question1\_pandas.py.

@@

	The above logic is implemented in function filter\_trips\_pandas. The two lists (trips\_too\_small and trips\_too\_big) will keep the excluded trips due to either not valid total distance or to invalid max distance between successive points. For each trip in the training dataset the total distance is calculated, using the function calculate\_lonlat\_distance, which returns the distance between two successive points using the haversine formula. Following the same logic, the max distance between successive points of a trip is calculated and a distance is found more than 2km, the trip is excluded.

	Finally, the distances are checked and rows with invalid trips are removed from the dataframe, which is afterwards exported in a new file (trips\_clean.csv).
